### 2021-07-16 manuscript/manuscript.Rnw
Minor changes

\begin{document}
\section{Introduction}
The 2020 Olympics (held in 2021) will feature the debut of five new sports (https://olympics.com/ioc/news/ioc-approves-five-new-sports-for-olympic-games-tokyo-2020): surfing, skateboarding, karate, baseball/softball (not really new, but absent since 2008) and sport climbing.  Sport climbing is particularly interesting as the International Olympic Committee (IOC) awarded only two sets of medals for the sport, one for men's and one for women's.

What makes this particularly interesting is that, sport climbing has several distinct disciplines: Speed climbing, bouldering, and lead climbing.  Speed climbing takes place on a standardized course and competitors try to reach the top of the course as fast as possible.  In the Olympics, speed climbing is being contested in a head-to-head format with ranks determined by how far a competitor advances in the bracket.   In bouldering, contestants have a fixed amount of time to complete as many courses as they can.  Winners are determined based on who completes the most courses and ties are broken based on who had the fewest attempts.  Ties are further broken by the competitor acheived the most ``zone holds", which are holds approximately half way through each course.  Finally, in lead climbing a competitor gets one point for each hold that they reach, so whoever reaches the highest point on the wall is the winner.  In lead climbing, each competitor only gets one attempt and when they fall their attempt is over.  %(https://www.cnet.com/news/climbing-at-the-tokyo-olympics-everything-you-need-to-know/)

@@

$$
Score_i = R^S_i \times R^B_i \times R^L_i
$$,

@@

Cross country scoring: %https://link.springer.com/content/pdf/10.1007/s11127-007-9193-6.pdf \cite{Hammond2007}

https://link.springer.com/article/10.1007/s11127-017-0494-0 \cite{BoudreauEtAl2018}

Decathlon scoring: %https://research.ou.nl/en/publications/decathlon-towards-a-balanced-and-sustainable-performance-assessme \cit{Westera2006}

@@

\subsection{Simulations}
\subsubsection{uniform ranks}

@@

 - So bouldering and lead as highly correlatd with each other.

@@

\section{Proposed better scoring method}
 - Rank sum

>>>>

\begin{document}
\section{Introduction}
The 2020 Summer Olympics (held in 2021) will feature the debut of five new sports (https://olympics.com/ioc/news/ioc-approves-five-new-sports-for-olympic-games-tokyo-2020): surfing, skateboarding, karate, baseball/softball (not really new, but absent since 2008) and sport climbing.  Sport climbing is particularly interesting as the International Olympic Committee (IOC) awarded only two sets of medals for the sport, one for men's and one for women's.

What makes this particularly interesting is that, sport climbing has several distinct disciplines: Speed climbing, bouldering, and lead climbing.  Speed climbing takes place on a standardized course and competitors try to reach the top of the course as fast as possible.  In the Olympics, speed climbing is being contested in a head-to-head format with ranks determined by how far a competitor advances in the bracket.   In bouldering, contestants have a fixed amount of time to complete as many courses as they can.  Winners are determined based on who completes the most courses and ties are broken based on who had the fewest attempts.  Ties are further broken by the competitor achieved the most ``zone holds", which are holds approximately half way through each course.  Finally, in lead climbing a competitor gets one point for each hold that they reach, so whoever reaches the highest point on the wall is the winner.  In lead climbing, each competitor only gets one attempt and when they fall their attempt is over.  %(https://www.cnet.com/news/climbing-at-the-tokyo-olympics-everything-you-need-to-know/)

@@

$$
Score_i = R^S_i\times R^B_i\times R^L_i
$$,

@@

Cross country scoring: %https://link.springer.com/content/pdf/10.1007/s11127-007-9193-6.pdf\cite{Hammond2007}

https://link.springer.com/article/10.1007/s11127-017-0494-0\cite{BoudreauEtAl2018}

Decathlon scoring: %https://research.ou.nl/en/publications/decathlon-towards-a-balanced-and-sustainable-performance-assessme\cit{Westera2006}

@@

\subsection{Simulations}
\subsubsection{Uniform ranks}

@@

- So bouldering and lead as highly correlated with each other.

@@

\section{Proposed better scoring method}

- Rank sum

### 2021-07-16 manuscript/manuscript.tex
Minor changes

\usepackage{alltt}
\usepackage{natbib}      % cross referencing bibliography entries
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{graphicx}    % importing graphics into figures
\usepackage{multirow}    % tables with multiple rows
\usepackage{slashbox}    % tables with slash
\usepackage{rotating}    % for vertical words in table
\usepackage{color}       % for textcolor.. (temporary use before submission)
\usepackage{bm}
\usepackage[section]{placeins} % ensure floats do not go into the next section.
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\section{Introduction}
The 2020 Olympics (held in 2021) will feature the debut of five new sports (https://olympics.com/ioc/news/ioc-approves-five-new-sports-for-olympic-games-tokyo-2020): surfing, skateboarding, karate, baseball/softball (not really new, but absent since 2008) and sport climbing.  Sport climbing is particularly interesting as the International Olympic Committee (IOC) awarded only two sets of medals for the sport, one for men's and one for women's.

What makes this particularly interesting is that, sport climbing has several distinct disciplines: Speed climbing, bouldering, and lead climbing.  Speed climbing takes place on a standardized course and competitors try to reach the top of the course as fast as possible.  In the Olympics, speed climbing is being contested in a head-to-head format with ranks determined by how far a competitor advances in the bracket.   In bouldering, contestants have a fixed amount of time to complete as many courses as they can.  Winners are determined based on who completes the most courses and ties are broken based on who had the fewest attempts.  Ties are further broken by the competitor acheived the most ``zone holds", which are holds approximately half way through each course.  Finally, in lead climbing a competitor gets one point for each hold that they reach, so whoever reaches the highest point on the wall is the winner.  In lead climbing, each competitor only gets one attempt and when they fall their attempt is over.  %(https://www.cnet.com/news/climbing-at-the-tokyo-olympics-everything-you-need-to-know/)

>>>>

\usepackage{alltt}
\usepackage{natbib}      % cross referencing bibliography entries
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{graphicx}    % importing graphics into figures
\usepackage{multirow}    % tables with multiple rows
\usepackage{slashbox}    % tables with slash
\usepackage{rotating}    % for vertical words in table
\usepackage{color}       % for textcolor.. (temporary use before submission)
\usepackage{bm}
\usepackage[section]{placeins} % ensure floats do not go into the next section.
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\section{Introduction}
The 2020 Summer Olympics (held in 2021) will feature the debut of five new sports (https://olympics.com/ioc/news/ioc-approves-five-new-sports-for-olympic-games-tokyo-2020): surfing, skateboarding, karate, baseball/softball (not really new, but absent since 2008) and sport climbing.  Sport climbing is particularly interesting as the International Olympic Committee (IOC) awarded only two sets of medals for the sport, one for men's and one for women's.

What makes this particularly interesting is that, sport climbing has several distinct disciplines: Speed climbing, bouldering, and lead climbing.  Speed climbing takes place on a standardized course and competitors try to reach the top of the course as fast as possible.  In the Olympics, speed climbing is being contested in a head-to-head format with ranks determined by how far a competitor advances in the bracket.   In bouldering, contestants have a fixed amount of time to complete as many courses as they can.  Winners are determined based on who completes the most courses and ties are broken based on who had the fewest attempts.  Ties are further broken by the competitor achieved the most ``zone holds", which are holds approximately half way through each course.  Finally, in lead climbing a competitor gets one point for each hold that they reach, so whoever reaches the highest point on the wall is the winner.  In lead climbing, each competitor only gets one attempt and when they fall their attempt is over.  %(https://www.cnet.com/news/climbing-at-the-tokyo-olympics-everything-you-need-to-know/)
